Study of the hadronization of charged pions

### 2017-03-23 1-Answers-Review.tex

4.
P16 - similarly, 1D fits for positive pion $\Delta\beta$?

{\it As the positive particles show much more apparent contamination sources than negative 
ones, we studied 
the TOF profile much more thoroughly. You can see in figures~\ref{TOF-1}, \ref{TOF-2} and 
\ref{TOF-3} the $\Delta \beta$ profiles for many momentum slices. In figure~\ref{TOF-1}
one can see some contamination from lighter leptons ($e+$ and $\mu^+$). These represent
a very small amount and one can see some justification for the choice of a $\pm 0.03$
cut as these particles do not appear to be discernable beyond that level. Similarly
in figure~\ref{TOF-2} one can see the contribution from kaons. The larger contribution
of this contamination motivated the tightening of the TOF cut on this side, to the limit
where kaons are a minority in the tail of the pion distribution. Finally a similar 
method is applied for the even larger proton contamination as shown in figure \ref{TOF-3}.
 (This paragraph and figures are added to the note)}\\

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
\caption {$\Delta \beta$ of positively charged particles for low momentum slices 
(GeV/c). The red lines shows the applied cuts to select positive pions. The bumps on the right
correspond to muon and electron masses.}
\label{TOF-1}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {answer-fig/TofProfile2.png} 
\caption {$\Delta \beta$ of positively charged particles for medium momentum slices 
(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
correspond to the kaon mass.}
\label{TOF-2}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {answer-fig/TofProfile3.png} 
\caption {$\Delta \beta$ of positively charged particles for high momentum slices 
(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
correspond to the proton mass.}
\label{TOF-3}
\end{figure}

@@

11.
P19, eq. 7 - Is it really just the sum of weights or are they the counts multiplied by the 
weights?

{\it They are indeed the counts multiplied by the weights.
The sum indicated runs over all the recorded events, it is not associated to the weight
bins or anything like that. We tried to adapt the language in the note to make it clearer.} \\

12.
P23, I’d be very worried about the MC modeling acceptance on falling edges like that at the 
right of the top right plot.

{\it It is indeed an important issue. A related fact to keep in mind (while it is presented 
later in the note in 2.5.1) is that the main issue there is the quantity of accidentals. Since
the cross section get really small in this region, accidentals start to overcome
the signal. We apply a cut
$p_\perp^2 < 2.5$ GeV$^2$/c$^2$ to remove these regions. One could advocate to lower this 
cut, but it would affect the outcome of the $\Delta P_\perp^2$, 
because as often with averages the outliers have a strong impact.

@@

17.
P27, Fig. 22 - the right column of plots is not the same as those in Fig. 15.  Why change the 
variables?

{\it Sorry, it is a mistake on our part, there is no reason. TO BE CORRECTED. And
add figures after radiative correction!} \\

18.
P28 - What is Coulolmb Correction applied to? Momentum of charged particles? Could you 
plot effect of this correction on particles? Is it really big enough to be visible within our 
resolutions ?

{\it The Coulomb correction is applied to incoming and outgoing electrons as well as
produced charged pions. Indeed the effect is small in most of the phase space, but 
by slightly shifting the $z$ distribution it slightly changes the normalization. A
point to point effect is also visible for low $z$ pions.

TODO Add figure as a function of A1/3 and z.} \\

@@

23.
P34, why do you have a 1\% normalization error in all the multiplicity ratios when you say just 
above that for this particular sample with two particles in the final state the events in the test 
regions dropped to 0.01?  Doesn’t that mean the target contamination normalization error is 
smaller than 1\%?

{\it Multiplicity ratios are a double ratio. The claim is that the semi inclusive part 
is not affected, but the inclusive electron ratio is affected. This is included
as a normalisation error. We revisited slightly the paragraph to make it clearer.} \\

24.
P34, with this technique of comparing results using the two different sets of variables (you 
call it two binnings, but I think that is sort of misleading), you are using the same events.  
Does this not mean you have a statistical contribution to this systematic error?  You say you 
noticed larger systematic errors for the pi- events due to lower acceptance and bigger 
weights.  Might it also be lower statistics and so you have statistical fluctuations contributing 
to the systematic error?  If so, you are sort of double-counting the statistical error and 
inflating the systematic error more than it should be.

{\it This is an interesting question and we might have overlooked this problem. We noted an error
in our function calculating the statistical errors. This change in size somewhat
modifies our initial statement,

TODO Complete the answer when full results are there.} \\

@@

25.
P35 - It would clarify the discussion with a summary or table of the point-to-point systematic 
errors.

{\it The point-to-point errors include only contributions from the particle 
identifications and acceptance effects. It is also different for every bin, so
we did not think a table would be useful to summarize only two contributions.} \\

### 2018-02-23 chap5.tex
Add notes on possible checks

>>>>

\subsection{Cross Checks}
\label{sec:XChecks}

The goal here is to check known results in order to make sure we have normalization right. This is 
especially important since discrepencies with Hayk's analysis have been found and demonstrated the 
normalization to be a tricky problem.

\subsubsection{Inclusive electron normalization}

We expect the EMC ratio to cross unity around 0.3 - 0.35 and we know precisely the target thickesses.
From these we check our inclusive normalization...

\subsubsection{Pion ratio from Hall-C}

In paper from Hall-C they present results shown in fig 20 (to reproduce here). The bin corresponds to 
1.5 < Q2 < 4 GeV2, 0.35 < xb < 0.45, 0.5 < z < 0.6 and Pt2 < 0.2. They find ratios of 0.556+-0.011 for pi+
and 0.520+-0.011 for pi-. Note that it is not a double ratio and should be affected by the EMC effect,
moreover they do not make an isospin correction which is 1.5\%.

Put my result here
